---
title: 'ISA 401 Final Project: Unstructured Data'
author: "Mia Weber, Victoria Rhodes, & Helen Kreitzer"
date: "2026-05-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Unstructured Data: School Course Catalog Pages

## Define Schema

```{r}
library(ellmer)

# initialize chat
chat = ellmer::chat_openai(model = "gpt-4o-mini")

# wrap schema
marketing_audit_schema = ellmer::type_array(
  items = ellmer::type_object(
    school_name = ellmer::type_string(),
    course_name = ellmer::type_string(),
    tech_score = ellmer::type_integer(
      description = "Score 1-10: 1 is pure theory/soft skills, 10 is heavy data/analytics/coding/SQL."
    ),
    skill_category = ellmer::type_string(
      description = "One of: 'Analytics', 'Digital/Social', 'Sales', 'Strategy', or 'Consumer Behavior'."
    ),
    tools_mentioned = ellmer::type_array(
      items = ellmer::type_string(),
      description = "List specific tools like Tableau, Salesforce, Google Analytics, Excel, etc."
    )
  )
)
```

## Structured Loop

```{r}
library(rvest)
library(ellmer)
library(dplyr)

# scrape messy text from htmls
get_school_text <- function(url) {
  html <- read_html(url)
  text <- html %>% 
    html_element("body") %>% 
    html_text2() 
  
  return(text)
}
```

## Extraction

```{r}
# urls from each school in one vector
school_urls <- c(
  "Miami" = "https://bulletin.miamioh.edu/farmer-business/marketing-bsb/",
  "OhioState" = "https://fisher.osu.edu/academic-departments/marketing-logistics/marketing/undergraduate-marketing/courses",
  "UC" = "https://www.business.uc.edu/faculty-research/marketing/degree-options/focus-areas.html",
  "OU" = "https://catalogs.ohio.edu/preview_program.php?catoid=104&poid=34215",
  "Toledo" = "https://catalog.utoledo.edu/undergraduate/courses/mktg/",
  "BGSU" = "https://catalog.bgsu.edu/preview_program.php?catoid=23&poid=8566",
  "Cleveland" = "https://business.csuohio.edu/academics/marketing-major",
  "Wright" = "https://business.wright.edu/supply-chain-management-marketing-and-management/marketing-course-descriptions",
  "Kent" = "https://catalog.kent.edu/coursesaz/mktg/",
  "Akron" = "https://bulletin.uakron.edu/undergraduate/colleges-programs/business-administration/marketing/marketing-management-bs/#requirementstext",
  "Youngstown" = "https://catalog.ysu.edu/courses/mktg/")

# initialize the LLM
chat = ellmer::chat_openai(model = "gpt-5-mini-2025-08-07")

all_school_data <- purrr::map_df(names(school_urls), function(name) {
  
  message("Processing: ", name)
  
  # scrape content
  raw_text <- get_school_text(school_urls[name])
  
  # send to LLM
  result <- chat$chat_structured(
    paste("Extract all Marketing courses from this text and grade them:", raw_text),
    type = ellmer::type_array(
      items = ellmer::type_object(
        course_name = ellmer::type_string(),
        tech_score = ellmer::type_integer(description = "1-10 tech/data focus"),
        skill_category = ellmer::type_string(description = "Analytics, Sales, etc."),
        tools = ellmer::type_array(items = ellmer::type_string())
      )
    )
  )
  
  # add school name to results
  result$school <- name
  return(result)
})
```

## Tech Score Average

```{r}
# calculate tech score average per school
score_averages <- all_school_data %>%
  group_by(school) %>%
  summarize(avg_tech_score = mean(tech_score),
            course_count = n())
```

## Top Skills and Tools

```{r}
library(tidyverse)

# create a dataset for top tools mentioned
top_tools <- all_school_data %>%
  unnest(tools) %>% 
  count(school, tools, name = "tool_count") %>%
  group_by(school) %>%
  slice_max(order_by = tool_count, n = 3, with_ties = FALSE) %>%
  summarize(top_3_tools = paste(tools, collapse = ", "))

# create a dataset for top skills mentioned
top_skills <- all_school_data %>%
  count(school, skill_category, name = "skill_count") %>%
  group_by(school) %>%
  slice_max(order_by = skill_count, n = 3, with_ties = FALSE) %>%
  summarize(top_3_skills = paste(skill_category, collapse = ", "))

# join tools, skills, and score averages into one dataset
school_curriculum_summary <- top_tools %>%
  left_join(top_skills, by = "school") %>%
  left_join(score_averages, by = "school")

print(school_curriculum_summary)
```



## Correct names and IDs

#### *Note: Wright State University was excluded from the curriculum extraction analysis because the course description content was dynamically loaded and could not be consistently extracted using the same static HTML workflow applied to the other universities*

```{r}
# mapping of school abbreviations to full name and ID
school_lookup <- data.frame(
  school = c("Akron", "BGSU", "UC", "Cleveland", "Kent", "Miami", 
             "OhioState", "OU", "Toledo", "Youngstown"),
  official_name = c("University of Akron Main Campus", 
                    "Bowling Green State University-Main Campus",
                    "University of Cincinnati-Main Campus", 
                    "Cleveland State University",
                    "Kent State University at Kent", 
                    "Miami University-Oxford",
                    "Ohio State University-Main Campus", 
                    "Ohio University-Main Campus",
                    "University of Toledo", 
                    "Youngstown State University"),
  id = c("200800", "201441", "201885", "202134", "203517", "204024", 
            "204796", "204857", "206084", "206695")
)

# join into one dataset
school_curriculum_summary <- top_tools %>%
  left_join(top_skills, by = "school") %>%
  left_join(score_averages, by = "school") %>%
  left_join(school_lookup, by = "school")

print(school_curriculum_summary)
```
## Output to CSV

```{r}
write.csv(
  school_curriculum_summary,
  "unstructured_curriculum.csv",
  row.names = FALSE
)
```



